Concave reduction in Self-Healing Swarms

### 2018-11-12 paper.tex
Updates
Abstract Tidy

\title{Concave reduction in Self-healing swarms}

@@

{Eliot \headeretal: Concave reduction in Self-healing swarms}
{Eliot \headeretal: Concave reduction in Self-healing swarms}

@@

Swarms consist of many agents that interact using a simple set of rules that create emergent behaviours. One such behaviour makes a swarm tolerant of failures. Failures occur for many reasons, for example; resource exhaustion, component failure, or a disruption from an external event. The loss of agents reduces the size of a swarm and may create an irregular structure. A swarm's structure can also be irregular due to initial conditions, loss of agents or due to an obstacle. These changes in the structure or size do not stop a swarm from functioning but can adversely affect the efficacy. This paper introduces and demonstrates emergent behaviour that can counter the effect of agent loss or irregular structures. The behaviour causes concave deformities to be removed. This technique is implemented by each agent identifying its position in relation to its neighbours. If the agent meets a defined criterion, based on the local geometry of the agent's neighbours to decide when an anomaly is present, the agent's `normal' movement is altered in such a way as to remove a gap between the neighbours. These changes in direction of agents cause the swarm, as a whole, to be reorganised into a more uniform structure with no internal voids.

@@

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to resolving swarm structure issues. A prototype framework for self-healing swarms was developed by Dai et al. which considered the problem of agent failure in hostile environments~\cite{DHMRZ:06}. This is in line with work carried out by Vassev and Hinchey who model swarm deployment using ASSL (Autonomic System Specification Language)~\cite{VH:09}. This technique was used by NASA (National Aeronautics and Space Administration) when developing their ANTS (Autonomous Nano Technology Swarm) for use in asteroid belt exploration. This line of research is more focused towards an agent's internal systems failure rather than the removal of anomalies in a swarm distribution. Roach et al. takes a different approach and focuses on the effects of sensor failure and the effect that has on agent distribution~\cite{RMT:15}. The closest research to concave reduction, as discussed in this paper, is that of Lee and Chong who identify the issue of concave edges within swarms in an attempt to create regular lattice formations~\cite{GN:08}. The main focus of their paper is the restructuring of the internal distribution of inter-agent formations. The research by Ismail and Timmis used the approach of \textit{bio-inspired} healing using \textit{granuloma formation}, a biological method for encapsulating an antigen~\cite{IT:10}.
Concave reduction is an extension of the work discussed by Ismail and Timmis in their paper on `self-healing' \cite{IT:10} and Lee and Chong's work on identifying concave edges~\cite{GN:08}. The technique also draws on the work of McLurkin and Demaine who have developed algorithms to detect perimeter types~\cite{MD:09}. The technique employed in this paper does not require the identification of the perimeter type as this would require a communications infrastructure.

\section{Swarm Model}\label{sec:Swarm Model}
To describe the removal of voids a swarming model needs to be defined. Equation~\ref{eq:BotPhysics1} defines a weighted model that includes cohesion, repulsion, direction and obstacle avoidance ($v_c(b), v_r(b), v_d(b), v_o(b)$). The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled to tailor the swarming effect.

@@

Now, we define for each agent $b$ a \textit{cohesion/repulsion scalar}, $P(b)$, to measure the influence of the neighbours of $b$ as cohesive (positive) or repulsive (negative); shown in Equation~\ref{eq:CohesionRepulsion}.

>>>>

\title{Concave reduction in Self-Healing Swarms}

@@

{Eliot \headeretal: Concave reduction in Self-Healing Swarms}
{Eliot \headeretal: Concave reduction in Self-Healing Swarms}

@@

Swarms consist of many agents that interact using a simple set of rules that create emergent behaviours. One such behaviour makes a swarm tolerant of failures. Failures occur for many reasons, for example: resource exhaustion, component failure, or a disruption from an external event. The loss of agents reduces the size of a swarm and may create an irregular structure. A swarm's structure can also be irregular due to initial conditions or due to an obstacle. These changes in the structure or size do not stop a swarm from functioning but can adversely affect its efficiency. This paper introduces and demonstrates local actions that cause an emergent behaviour that can counter the effect of agent loss or structural irregularity. This technique is implemented by each agent identifying its position in relation to its neighbours. If an agent meets an anomaly criterion, defined by the local geometry of its neighbours, the agent's `normal' movement is altered to remove the anomaly. These changes in movement cause the swarm, as a whole, to be reorganised into a more uniform structure.

@@

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to resolving swarm structure issues. A prototype framework for self-healing swarms was developed by Dai et al. which considered the problem of agent failure in hostile environments~\cite{DHMRZ:06}. This is in line with work carried out by Vassev and Hinchey who model swarm deployment using ASSL (Autonomic System Specification Language)~\cite{VH:09}. This technique was used by NASA (National Aeronautics and Space Administration) when developing their ANTS (Autonomous Nano Technology Swarm) for use in asteroid belt exploration. This line of research is more focused towards an agent's internal systems failure rather than the removal of anomalies in a swarm distribution. Roach et al. takes a different approach and focuses on the effects of sensor failure and the effect that has on agent distribution~\cite{RMT:15}. The closest research to concave reduction, as discussed in this paper, is that of Lee and Chong who identify the issue of concave edges within swarms in an attempt to create regular lattice formations~\cite{GN:08}. The main focus of their paper is the restructuring of the internal distribution of inter-agent formations. The research by Ismail and Timmis used the approach of \textit{bio-inspired} healing using \textit{granuloma formation}, a biological method for encapsulating an antigen~\cite{IT:10}. They also consider the effects failed agents can have upon a swarm when traversing a terrain \cite{TIBW:16}. 
Concave reduction is an extension of the work discussed by Ismail and Timmis in their papers on `self-healing' \cite{IT:10} and the effects of failed agents \cite{TIBW:16}. It also builds upon Lee and Chong's work on identifying concave edges~\cite{GN:08}. The technique also draws on the work of McLurkin and Demaine who have developed algorithms to detect perimeter types~\cite{MD:09}. The technique employed in this paper does not require the identification of the perimeter type as this would require a communications infrastructure.

\section{Swarm Model}\label{sec:Swarm Model}
To describe the removal of voids a swarming model needs to be defined. The model use is the same as that defined by Eliot et. al. in their paper that introduces a new magnitude based metric~\cite{EKB:18}. Equation~\ref{eq:BotPhysics1} defines a weighted model that includes cohesion, repulsion, direction and obstacle avoidance ($v_c(b), v_r(b), v_d(b), v_o(b)$). The weightings $k_c, k_r, k_d, k_o$ allow each component to be scaled to tailor the swarming effect.

@@

The metric used to analyse the swarm changes are defined by Eliot et. al. in~\cite{EKB:18}. Each agent $b$ can be analysed based upon a \textit{cohesion/repulsion scalar}, $P(b)$, to measure the influence of the neighbours of $b$ as cohesive (positive) or repulsive (negative) as shown in Equation~\ref{eq:CohesionRepulsion}.
